# Reproducible Research: Peer Assessment 1
setwd("/Documentation/Video Trainings/InProgress/Data Science Track/Reproducible Research/Assignments/AS1/RepData_PeerAssessment1")

## Loading and preprocessing the data
```{r}
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date)
summary(activity)
steps_per_day <- aggregate(steps~date,data=activity, sum)
```

## What is mean total number of steps taken per day?
```{r}
mean(steps_per_day$steps, na.rm=T)
```
### Median total number of steps, taken per day:
```{r}
median(steps_per_day$steps,na.rm=T)
```
## What is the average daily activity pattern?
```{r}
int.steps <- aggregate(steps~interval,data=activity, mean)
plot(int.steps$interval, int.steps$steps, type="l", xlab="Interval", ylab="Steps", main="Time series plot")
```


## Imputing missing values
```{r}
ok <- complete.cases(activity)
sum(!ok)
imputed <- activity
imputed[!ok,]$steps <- int.steps[!ok,]$steps
iint.steps <- aggregate(steps~interval,data=imputed,mean)
plot(iint.steps$interval, iint.steps$steps, type="l", xlab="Interval", ylab="Steps", main="Time series plot")
mean(int.steps$steps,na.rm=T)
mean(iint.steps$steps,na.rm=T)

```

## Are there differences in activity patterns between weekdays and weekends?
```{r echo = TRUE}

activity$wdays <- ifelse(weekdays(activity$date) %in% c("Saturday", "Sunday"), "weekend", "weekday")
steps <- aggregate(steps~interval+wdays, data=activity, mean)
library(lattice)
xyplot(steps~interval|wdays, data=steps, type = "l", layout=c(1,2), xlab="Interval", ylab="Number of steps")
```
;
